### 2020-01-31 wuhan.tex
deleting comments
Tighten abstract

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have prioritized estimating the basic reproductive number \Ro, defined as the average number of secondary cases caused by a primary case.
While these efforts are extremely valuable, their modeling approaches and the resulting estimates vary widely.
Here, we present a framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.
